Wireless Automobile Detection, License Plate Processing, and Data Availability Network

### 2014-04-30 paper/paper.tex

\usepackage{setspace}
\setstretch{1.5}
\usepackage{enumerate}

@@

\subsubsection{Test Data Collection}
{\color{red}\textbf{NOT COMPLETE}}
??? WHERE TO DISCUSS ACTUAL COLLECTION OF TEST DATA???

@@

Intrada requires a username and password to process images. The SOAP API allows for the sending of the username and password as part of each request object for authentication. Then, Intrada runs their proprietary algorithm on its own servers before returning a result string back to our web application. The result string contains helpful

\subsubsection{Evaluation Results}
{\color{red}\textbf{NOT COMPLETE}}

@@

\subsection{Web Application}
{\color{red}\textbf{NOT COMPLETE}}
\begin{figure}
\begin{center}
\includegraphics[width=5in]{schema}
\end{center}
\caption{MySQL Database Schema}
\label{fig:schema}
\end{figure}
As mentioned in section 1.2, the ACMx group has already created a web application that will display the data collected from the sensors in the system. The site is currently accessible online at \url{http://acmxlabs.org/parking/}. Since the current site is essentially just a shell with no data, one main goal of this project is to make the main pages of the site fully functional. Another main goal is to create an administrator side to the site, where data can be viewed and updated by site administrators. The main focus of this subsystem will be to provide interfaces for both general users and administrators that make the data we collect both useful and easy to access. Since the ACMx team already has some protocols in place for collecting and displaying the data from the magnetometer Arduino Fios, the ACMx team will continue development on this interface, and our group will focus on other parts of the application, as described below. The web application itself will be written with PHP on the back end and HTML5/CSS3/JavaScript on the front end. The following subsections describe the various pieces of the site that we aim to complete during this project.

>>>>

\usepackage{setspace}
\setstretch{1.5}
\usepackage{enumerate}
\usepackage{paralist}

@@

\subsubsection{Test Data Collection}
{\color{red}\textbf{NOT COMPLETE}}
In order to evaluate the ALPR platforms, we needed to collect test data. Both platforms were already trained to run North American license plates out-of-the-box, so the stage was set to process images for a comparison in performance. With our final deployment in mind, we also wanted to collect images from a variety of different angles and distances, as the resulting evaluation will help determine the best camera placement in the CTLM parking lot. To accurately test the ALPR programs for our project, the test images need to be taken with the same camera that would be used during deployment.

We loaded a special testing script written in Python onto a Raspberry Pi to accomplish this task. The script was programmed to wait for a hardware interrupt before taking an image. We wired a button via a breadboard to provide the hardware interrupt. Our team brought this Pi, camera, and button out to the CTLM parking lot and positioned it near where it would be deployed.

Once powered on, we had one teammate drive their car in and out of the parking lot multiple times. While he was driving, two other team members operated the camera and breadboard hardware to take images. Using the same license plate for this portion of our test data acquisition was intentional to lower the number of uncontrolled variables in gathering data.

Besides images of the same license plate, we also collected several images of nearby parked cars, as well as cars that entered or exited the CTLM parking lot during that time period. And because our system is to be deployed on a college campus, we also collected images from different states, as the population of nonresidents is much greater here than in neighboring small towns.

Overall, we were able to collect 56 images of seven different plates that contained recognizable numbers. Each image from the Raspberry Pi camera was about 3 megabytes in size in its uncompressed form. The Python script also specified that the camera should save in a JPEG (.jpg) format.

The data set, which we will now refer to as the \emph{Unaltered Data Set}, is the basis for all other data sets in this paper. That is, all other data sets are derived from these original, uncompressed images.

@@

Intrada requires a username and password to process images. The SOAP API allows for the sending of the username and password as part of each request object for authentication. Then, Intrada runs their proprietary algorithm on its own servers before returning a result string back to our web application. The result string contains colon delimited fields that carry 
\begin{inparaenum}[\itshape a\upshape)]
\item the extracted license plate characters;
\item the confidence in the extraction;
\item the state of origin of the license plate;
\item the confidence in the state of origin;
\item coordinates of the boundary box of the detected license plate; and
\item the execution time for the specified image.
\end{inparaenum}

\subsubsection{ALPR Evaluation Environment}
The ALPR software is

@@

\subsection{Web Application}
{\color{red}\textbf{NOT COMPLETE}}
As mentioned in section 1.2, the ACMx group has already created a web application that will display the data collected from the sensors in the system. The site is currently accessible online at \url{http://acmxlabs.org/parking/}. Since the current site is essentially just a shell with no data, one main goal of this project is to make the main pages of the site fully functional. Another main goal is to create an administrator side to the site, where data can be viewed and updated by site administrators. The main focus of this subsystem will be to provide interfaces for both general users and administrators that make the data we collect both useful and easy to access. Since the ACMx team already has some protocols in place for collecting and displaying the data from the magnetometer Arduino Fios, the ACMx team will continue development on this interface, and our group will focus on other parts of the application, as described below. The web application itself will be written with PHP on the back end and HTML5/CSS3/JavaScript on the front end. The following subsections describe the various pieces of the site that we aim to complete during this project.
